Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-21 Thesis/chapter/060-results-material.tex
XRD and SEM text frist draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SEM}
\begin{figure}
    \centering
    \begin{subfigure}{.4\textwidth}
        \includegraphics[width=\textwidth]{Pics/sem/071_fto_old_1x.png}
        \caption{sem1}
        \label{fig:sem1}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
        \includegraphics[width=\textwidth]{Pics/sem/071_fto_old_2x.png}
        \caption{sem2}
        \label{fig:sem2}
    \end{subfigure}
    \caption{sem}
    \label{fig:sem}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I and preoptimization}
The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 
was varied during preoptimization. 
The slower the \gls{db} velocity the more \td{homogeneously} the solution evaporated. 
If the \gls{db} was \td{too slow (lt 1 mm/s)} the surface tension pulled solvent over the sample without \td{leaving was zurk/forming a gel.}
\td{deposition because miniscus is pulling liquid off the substrate.}
Additionally the temperature while doctor blading affects the resulting layer together with the \gls{db} velocity.

\td{Assumption: Ideally solution evaporate shortly after DB but not before}
due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-good-10x1F.png}
        \caption{log} \label{fig:log1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-okay-3x4F.png}
        \caption{log} \label{fig:log2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log} \label{fig:log3}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat} \label{fig:stat1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat} \label{fig:stat2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat} \label{fig:stat3}
    \end{subfigure}
    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:sem}
\end{figure}

>>>>

In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
This wideness is is due to polycristalinity/amorphness of the material which is \td{erwartet due} to the sol-gel creation process.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SEM}
\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
        \caption{71 fto old 1x} \label{fig:sem-old1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
        \caption{71 fto old 2x} \label{fig:sem-old2}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
        \caption{115 fto cs 1x} \label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \caption{147 steel ph? 10x} \label{fig:sem-ph}
    \end{subfigure}
    \caption{sem}
    \label{fig:sem}
\end{figure}

The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
and the quality of the picture relies on the conductance of the material's surface. 
This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
Figure \ref{fig:sem-old} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
also/even after several/multiple/various alteration to the recipe.

Figure \ref{fig:sem-cs1} shows the cross section of a single layers of \gls{zro} on \gls{fto} glass. 
The large crystalline \td{range} which makes up most of the topper/top part of the image is \gls{fto}. 
The úbergang to glass is gerade noch so zu sehen. 
On the lower kante of the \gls{fto} a circa 100nm thick homogeneous layer can be observed, \gls{zro} produced by buthanolic recipe inspired by Hu et al..

Figure \ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic layer on top of a steel substrate. 
The large unregularity on the bottom left could darstellen a pin hole a (tiny) hole that reaches the substrate. 
These unregularites are rather the ausnahme. 
Alternatively, the small, hardly visible  irregularities verstreut across surface could darstellen such pin holes. 
These - I think - eher only are one layer deep irregularities since they are so haeufig 
and very little pin holes were observed on similar samples.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I}
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-good-10x1F.png}
        \caption{log} \label{fig:log1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-okay-3x4F.png}
        \caption{log} \label{fig:log2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log} \label{fig:log3}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat} \label{fig:stat1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat} \label{fig:stat2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat} \label{fig:stat3}
    \end{subfigure}
    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:iv}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preoptimization}
The doctor blading velocity (i.e. the velocity with which the blade moves and spreads the sol over the sample) 
was varied during preoptimization. 
The slower the \gls{db} velocity the more \td{homogeneously} the solution evaporated. 
If the \gls{db} was \td{too slow (lt 1 mm/s)} the surface tension pulled solvent over the sample without \td{leaving was zurk/forming a gel.}
\td{deposition because miniscus is pulling liquid off the substrate.}
Additionally the temperature while doctor blading affects the resulting layer together with the \gls{db} velocity.

\td{Assumption: Ideally solution evaporate shortly after DB but not before}
due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation

### 2022-10-21 Thesis/chapter/061-results-emma.tex
XRD and SEM text frist draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{what is best}
\begin{align}
%    G    & = -3.7 + 0.18 * TCal +  8.1 * max(0,6-layr)\\
%    \rho & = -0.78 + 0.0024 * TCal + 0.13 * max(0,6-layr)
    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
\end{align}
what was the best result? For each particle there is best and global best. 
https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{how did model selection influence results}
\begin{itemize}
    \item MARS chooses same set from independent variables for predicting all dependent variables. 
    \item flaws of MARS: all functions are dependent on same indep vars
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search 
    \item KRR (???)
    \item SVM (???)
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{what is best}
\begin{align}
%    G    & = -3.7 + 0.18 * TCal +  8.1 * max(0,6-layr)\\
%    \rho & = -0.78 + 0.0024 * TCal + 0.13 * max(0,6-layr)
    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
    \label{eq:emma}
\end{align}
what was the best result? For each particle there is best and global best. 
https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{how did model selection influence results}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ were included as dependent variable with the objective to maximize with a relative weight of 0.05.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the alogrithm would correctly predict those. 
Two major flaws behind this flaws became obvious with time: 
(1) The algorithm would be influenced by those values to choose samples, which potenitally optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
Neben making the problem unnoetiger weise more complicate, important time (around 10\% of the samples) could have been replaced with more insighful samples. 
(2) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ ($C/h$ instead of $C/min$) and $\lambda$, respectively. 
The algorithm will tend to include thos values into the prediction function for all dependent variables and possibly exclude others which have more influence on $G$ and $\rho$ (see \ref{eq:emma}).
\begin{itemize}
    \item MARS chooses same set from independent variables for predicting all dependent variables. 
    \item flaws of MARS: all functions are dependent on same indep vars
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performes (or rather, more precisely MARS)
It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
Anova shows that the influence of TCal is significant as shown by the F 
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search 
    \item KRR (???)
    \item SVM (???)
\end{itemize}
